Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-07-25 README.qmd
Add link to Docker repo

To reproduce the findings and re-run the analysis, do the following:

>>>>

To replicate the findings and re-run the analysis, you can use a Docker container at [`mountainous-mackerel-docker`](https://github.com/andrewheiss/mountainous-mackerel-docker), which will create a complete computing envirionment for running everything. Full details and instructions [are available there](https://github.com/andrewheiss/mountainous-mackerel-docker).

Alternatively, everything can be run on your local computer too. Do the following:
